Methods paper for erosion

### 2017-09-27 docs/methods/erosion_methods.tex
In methods paper, corrected sign in the erosion law (since n points inwards)
Made some small changes to the methods tex file.

This is a methods paper
\begin{itemize}
  \item Boundary integral equation formulation
  \item How we compute the shear stress and pressure
  \item Multiple bodies
  \item Avoiding stokes paradox
  \item \thL formulation
  \item Regularization
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation\label{s:formulation}} 
Let us first define the main variables used to model erosion.  We only
consider flows that are confined by a solid wall $\Gamma$ that encloses
$M$ eroding bodies.  The bodies are denoted as $\gamma_k$,
$k=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup
\gamma_M$.  Neglecting inertial forces, the dynamics of the fluid is
fully characterized by the position of the bodies $\xx_k(s,t) \in
\gamma_k$, where $s$ is the arclength and $t$ is time.  Given
$\xx_k(s,t)$, $k=1,\ldots,M$, derived variables include the fluid
velocity $\uu$, the pressure $p$, and the shear stress $\tau$.   On the
bounding wall, we prescribed a velocity $\UU(\xx,t)$.  Then, the
governing equations are
\begin{equation}
\label{eqn:erosionModel}
\begin{split}
  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{conservation
of momentum}\\
\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap
&&\mbox{conservation of mass} \\
\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{no slip on the
bodies} \\
\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{outer wall
velocity} \\
\dot{\xx}(t) = -|\tau| \nn, &\hspace{20pt} \xx \in \gamma,
&&\mbox{erosion model},
\end{split}
\end{equation}
where $\nn$ is the outward unit normal vector which points away from the
fluid.  The outer wall is formed by rounding off the corners of $[-3,3]
\times [-1,1]$, and we enforce the Hagen-Poiseuille flow
\begin{align*}
  \uu(\xx) = (1-y^2,0)
\end{align*}
on $\Gamma$.  The boundary of the fluid domain is $\bd\Omega = \gamma_1
\cup \cdots \cup \gamma_M \cup \Gamma$.  To minimize the boundary
effects of the inflow and outflow, we only place bodies in the center
third, $[-1,1] \times [-1,1]$, of the fluid domain.
\begin{figure}[htpb]
  \centering
  \input{figs/schematic.tikz}
  \caption{\label{fig:schematic} A schematic for the governing
    equations.  A no-slip boundary condition is imposed on each body
    $\gamma_k$ whose unit normal points outward relative to the
    geometry.  On the outer geometry $\Gamma$, a pipe flow is imposed.
    The bodies are eroded according to the shear stress applied by the
    Stokesian fluid.  Finally, the bodies are constrained to the middle
    third of the channel that is located between the dashed lines.}
\end{figure}

@@

To model erosion, we the normal velocity is prescribed to be
proportional to the absolute value of the shear stress.  The constant of
proportionality sets the time scale, and we set its value to be -1
\begin{align}
  \dot{\xx}(t) = -|\tau| \nn.
  \label{eqn:bodyEvolution}
\end{align}

@@

Once the shear stress is computed, it is used to update the shape of the
bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
eliminate tangling and stretching of the mesh, we use a \thL
formulation~\cite{hou-low-she1994} which is described in
Section~\ref{sec:thetaL}.  In this section, we also describe our time
stepping method and two regularization terms that are necessary to
control the curvature of the bodies and to maintain spectral accuracy in
space.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\thL Formulation} 
\label{sec:thetaL}

@@

\vsp{2}
To handle boundary evolution, we use the \thL    method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems. Throughout this section, we use the following conventions: the bodies are parametrized in the CCW direction and the normal vector points into the bodies (our out of the fluid).

\todo[inline]{BRYAN: Can we use these conventions throughout the paper?}

In order to regularize boundary evolution, we modify
Eq.~(\ref{eqn:bodyEvolution}) to include a curvature-driven component
(also corrected errors in this equation)
\begin{equation}
\pderiv{\xx}{t} = |\tau| \nn + \eps \elfun(L) \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
The curvature term acts to smooth bodies that have high-frequency oscillations.

>>>>

This is a methods paper
\begin{itemize}
  \item Boundary integral equation formulation
  \item How we compute the shear stress and pressure
  \item Multiple bodies
  \item Avoiding stokes paradox
  \item {\thL} formulation
  \item Regularization
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation\label{s:formulation}} 
Let us first define the main variables used to model erosion.  We only
consider flows that are confined by a solid wall $\Gamma$ that encloses
$M$ eroding bodies.  The bodies are denoted as $\gamma_k$,
$k=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup
\gamma_M$.  Neglecting inertial forces, the dynamics of the fluid is
fully characterized by the position of the bodies $\xx_k(s,t) \in
\gamma_k$, where $s$ is the arclength and $t$ is time.  Given
$\xx_k(s,t)$, $k=1,\ldots,M$, derived variables include the fluid
velocity $\uu$, the pressure $p$, and the shear stress $\tau$.   On the
bounding wall, we prescribed a velocity $\UU(\xx,t)$.  Then, the
governing equations are
\begin{equation}
\label{eqn:erosionModel}
\begin{split}
  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{conservation
of momentum}\\
\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap
&&\mbox{conservation of mass} \\
\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{no slip on the
bodies} \\
\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{outer wall
velocity} \\
\dot{\xx}(t) = \abs{\tau} \nn, &\hspace{20pt} \xx \in \gamma,
&&\mbox{erosion model},
\end{split}
\end{equation}
where $\nn$ is the outward unit normal vector which points away from the
fluid.  The outer wall is formed by rounding off the corners of $[-3,3]
\times [-1,1]$, and we enforce the Hagen-Poiseuille flow
\begin{align*}
  \uu(\xx) = (1-y^2,0)
\end{align*}
on $\Gamma$.  The boundary of the fluid domain is $\bd\Omega = \gamma_1
\cup \cdots \cup \gamma_M \cup \Gamma$.  To minimize the boundary
effects of the inflow and outflow, we only place bodies in the center
third, $[-1,1] \times [-1,1]$, of the fluid domain.
\begin{figure}[htpb]
  \centering
  \input{figs/schematic.tikz}
  \caption{\label{fig:schematic} A schematic for the governing
    equations.  A no-slip boundary condition is imposed on each body
    $\gamma_k$ whose unit normal points outward relative to the
    geometry.  On the outer geometry $\Gamma$, a pipe flow is imposed.
    The bodies are eroded according to the shear stress applied by the
    Stokesian fluid.  Finally, the bodies are constrained to the middle
    third of the channel that is located between the dashed lines.}
\end{figure}

@@

To model erosion, we the normal velocity is prescribed to be
proportional to the absolute value of the shear stress.  The constant of
proportionality sets the time scale, and we set its value to be -1
\begin{align}
  \dot{\xx}(t) = \abs{\tau} \nn.
  \label{eqn:bodyEvolution}
\end{align}

@@

Once the shear stress is computed, it is used to update the shape of the
bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
eliminate tangling and stretching of the mesh, we use a {\thL}
formulation~\cite{hou-low-she1994} which is described in
Section~\ref{sec:thetaL}.  In this section, we also describe our time
stepping method and two regularization terms that are necessary to
control the curvature of the bodies and to maintain spectral accuracy in
space.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\thL} Formulation} 
\label{sec:thetaL}

@@

\vsp{2}
To handle boundary evolution, we use the {\thL}    method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems. Throughout this section, we use the following conventions: the bodies are parametrized in the CCW direction and the normal vector points into the bodies (our out of the fluid).

In order to regularize boundary evolution, we modify
Eq.~(\ref{eqn:bodyEvolution}) to include a curvature-driven component
(also corrected errors in this equation)
\begin{equation}
\dot{\xx}(t) = \abs{\tau} \nn + \eps \elfun(L) \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
The curvature term acts to smooth bodies that have high-frequency oscillations.

Simple form for my talk
\begin{equation}
\dot{\xx}(t) = \abs{\tau} \nn + \eps \kappa
\end{equation}
